Geometrization of the local Langlands correspondence for algebraic tori

### 2014-05-30 dictionary.tex
Working on geometrization

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% AMS packages
\usepackage{amsmath, amsthm, amssymb, todonotes}% showkeys}
\usepackage[alphabetic]{amsrefs}
% Fonts
\usepackage{mathrsfs, yfonts}
\usepackage{geometry}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

\begin{proposition}\label{prop:basechange}
 The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
 defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
 Moreover, the following diagram commutes:
\[
\begin{tikzcd}[column sep=60]
\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
G(k)^*  \rar{\Nm^*} & G(k')^*.
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
\[
\begin{tikzcd}
\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
\end{tikzcd}
\]
Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
\end{proof}

@@

\begin{proposition}
The following diagram of isomorphisms commutes, where the bottom map is the identity:
\[
\begin{tikzcd}
\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
G'(k')^* \rar & G'(k')^*
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
\[
(\Res_{k'/k}G')(k') \to G'(k')^*
\]
induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
\[
(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
\]
is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
\end{proof}

@@

\begin{corollary}\label{cor:exact}
  If $G$ is a smooth, commutative group scheme over
  $\Fq$ then pullback yields an exact sequence
\[
0 \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
\]
of abelian groups.
\end{corollary}

>>>>

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% AMS packages
\usepackage{amsmath, amsthm, amssymb, todonotes}% showkeys}
\usepackage[alphabetic]{amsrefs}
% Fonts
\usepackage{mathrsfs, yfonts}
%Geometry
\usepackage{geometry}
% Enumitem
%\usepackage{enumitem}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

\begin{proposition}\label{prop:basechange}
With notation above,
the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
 defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
 Moreover, the following diagram commutes:
\[
\begin{tikzcd}[column sep=60]
\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
G(k)^*  \rar{\Nm^*} & G(k')^*.
\end{tikzcd}
\]
\end{proposition}

\todo{The bottom arrow is an isomorphism to $G(k')^*_{\Gal(k'/k)}$. We will see that the horizontal arrows are isomorphisms on loose quasicharacter sheaves. Can we make sense of $\QC(G_{k'})_{\Gal(k'/k)}$? If so, is the functor $\nu_{k'/k}$ into $\QC(G_{k'})_{\Gal(k'/k)}$ an equivalence of categories?}

\begin{proof}
Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
\[
\begin{tikzcd}
\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
\end{tikzcd}
\]
Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
\end{proof}

@@

\begin{proposition}
Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
The following diagram of isomorphisms commutes, where the bottom map is the identity:
\[
\begin{tikzcd}
\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
G'(k')^* \rar & G'(k')^*
\end{tikzcd}
\]
\end{proposition}
\begin{proof}
By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
\[
(\Res_{k'/k}G')(k') \to G'(k')^*
\]
induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
\[
(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
\]
is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
\end{proof}

\todo{Can we improve on this result by proving that $\rho$
is an equivalence of categories?}

@@

\begin{corollary}\label{cor:exact}
  If $G$ is a smooth, commutative group scheme over
  $\Fq$ then pullback yields an exact sequence
\[
0 \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
\]
of abelian groups.\todo{Pure speculation.}
\end{corollary}

### 2014-05-30 geometrization.tex
Working on geometrization

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% AMS packages
\usepackage{amsmath, amsthm, amssymb}
\usepackage[alphabetic]{amsrefs}
\usepackage{todonotes}
% Fonts
\usepackage{mathrsfs, yfonts}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

%%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\dual}[1]{{\hat{#1}}}
%% Limits
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
%% Fonts for quasicharacter sheaves
\newcommand{\qcs}[1]{{\mathcal{#1}}}
\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
%% Categories
\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
\newcommand{\QCb}{{\QC_0}}
\newcommand{\QCf}{{\QC_f}}
\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
\newcommand{\trFrob}[1]{t_{#1}}
\newcommand{\TrFrob}[1]{T_{#1}}
%% amsmath replacements for \atop
\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
%% Labeled items
\makeatletter
\newcommand{\labitem}[2]{
\def\@itemlabel{\textbf{#1}}
\item
\def\@currentlabel{#1}\label{#2}}
\makeatother
%% Shorthand for bars
\renewcommand{\bf}{\bar{f}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bm}{\bar{m}}
\newcommand{\bG}{\bar{G}}
\newcommand{\bH}{\bar{H}}
%% Spacing control
\newcommand{\tight}[3]{\hspace{-#1pt}{#2}\hspace{-#3pt}}
\newcommand{\GxG}{\text{$G \tight{1}{\times}{1} G$}}
\newcommand{\bGxG}{\text{$\bar{G} \tight{1}{\times}{1} \bar{G}$}}
\newcommand{\bfxf}{\text{$\bar{f} \tight{1}{\times}{1} \bar{f}$}}
\newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
\newcommand{\LxL}{\text{$\gqcs{L} \tight{0}{\boxtimes}{0} \gqcs{L}$}}
\newcommand{\ExE}{\text{$\qcs{E}\tight{0}{\boxtimes}{0}\qcs{E}$}}
\newcommand{\bExE}{\text{$\gqcs{E}\tight{0}{\boxtimes}{0}\gqcs{E}$}}
\newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
\newcommand{\BxB}{\text{$B \tight{1}{\times}{1} B$}}
\newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
%% Margin notes
\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
%% Hyphenation override
\hyphenation{quasi-character}

%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
\begin{document}

@@

In this paper we explain how to geometrize quasicharacters of algebraic tori over local fields.
%
Let $K$ be a non-archimedian local field
with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
is a smooth group scheme over $\OK$ with generic fibre $T$ and a canonical isomorphism
$\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$. Then $\GN{T}_n$ is a smooth commutative group scheme over $\Fq$; as such, it carries the category $\QC(\GN{T}_n)$ of quasicharacter sheaves, introduced in \cite{cunningham-roe:dictionary}. The main result in this paper, Theorem~\ref{thm:application}, provides a functorial translation of characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
\[
\QCiso{\GN{T}_n}
\iso
\Hom_{< n}(T(K),\EEx).
\]
We also describe a pro-group scheme $\GN{T}$
simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.

\[
\begin{tikzcd}
\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr} & \\
\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell)
\end{tikzcd}
\]

While we have not yet fully explored the applications of such a geometrization, we want to highlight
some of the potential benefits of Theorem~\ref{thm:application} here.
Characters on $T$ have limited
functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
in the presence of maps from $T$ to other groups.  Sheaves, on the other hand, come
equipped with a host of functors, including pushforward.
We hope to use this to our advantage as we work toward an adaptation of
Lusztig's theory of characters sheaves to the study of characters of
admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.

@@

\section{Quasicharacters of algebraic tori over local fields}

@@

\section{Greenberg of N\'eron}
\label{sec:GN}

@@

\section{The function--sheaf dictionary for quasicharacters of bounded depth}\label{sec:qcs}

In \cite{cunningham-roe:dictionary} we extended the function--sheaf dictionary of Deligne  \cite{deligne:SGA4.5}*{sommes trig.} to smooth commutative group schemes locally of finite type over finite fields for which the geometric component group is finitely generated.
Since we will use this dictionary here, we briefly review the main notation and result from that paper.

Let $G$ be a smooth commutative group schemes locally of finite type over $\Fq$ for which the geometric component group is finitely generated. A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; see \cite{cunningham-roe:dictionary}.
%
Quasicharacter sheaves on $G$ form a rigid monoidal category, denoted by $\QC(G)$
and the trace of Frobenius
\begin{equation}\label{snake}
  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
\end{equation}
  is a functorial isomorphism of groups \cite{cunningham-roe:dictionary}*{Thm. 11.1}.

@@

\section{A function--sheaf dictionary for quasicharacters} \label{sec:quasichar}

@@

\section{Restriction of scalars over local fields}
\label{sec:wrK}

@@

\section{Transfer of quasicharacter sheaves} \label{sec:transfer}

\section{Toward geometric reciprocity for tori over local fields}
\label{sec:reciprocity}

@@

\end{document}
%sagemathcloud={"zoom_width":90}

>>>>

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% AMS packages
\usepackage{amsmath, amsthm, amssymb, geometry}
\usepackage[alphabetic]{amsrefs}
\usepackage{todonotes}
% Fonts
\usepackage{mathrsfs, yfonts}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

%%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\dual}[1]{{\hat{#1}}}
%% Limits
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
%% Fonts for quasicharacter sheaves
\newcommand{\qcs}[1]{{\mathcal{#1}}}
\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
%% Categories
\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
\newcommand{\QCb}{{\QC_0}}
\newcommand{\QCf}{{\QC_f}}
\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
\newcommand{\trFrob}[1]{t_{#1}}
\newcommand{\TrFrob}[1]{T_{#1}}
%% amsmath replacements for \atop
\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
%% Labeled items
\makeatletter
\newcommand{\labitem}[2]{
\def\@itemlabel{\textbf{#1}}
\item
\def\@currentlabel{#1}\label{#2}}
\makeatother
%% Shorthand for bars
\renewcommand{\bf}{\bar{f}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bm}{\bar{m}}
\newcommand{\bG}{\bar{G}}
\newcommand{\bH}{\bar{H}}
%% Spacing control
\newcommand{\tight}[3]{\hspace{-#1pt}{#2}\hspace{-#3pt}}
\newcommand{\GxG}{\text{$G \tight{1}{\times}{1} G$}}
\newcommand{\bGxG}{\text{$\bar{G} \tight{1}{\times}{1} \bar{G}$}}
\newcommand{\bfxf}{\text{$\bar{f} \tight{1}{\times}{1} \bar{f}$}}
\newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
\newcommand{\LxL}{\text{$\gqcs{L} \tight{0}{\boxtimes}{0} \gqcs{L}$}}
\newcommand{\ExE}{\text{$\qcs{E}\tight{0}{\boxtimes}{0}\qcs{E}$}}
\newcommand{\bExE}{\text{$\gqcs{E}\tight{0}{\boxtimes}{0}\gqcs{E}$}}
\newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
\newcommand{\BxB}{\text{$B \tight{1}{\times}{1} B$}}
\newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
%% Margin notes
\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
%% Hyphenation override
\hyphenation{quasi-character}
\hyphenation{quasi-characters}
%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
\begin{document}

@@

This paper provides a geometric proof of the local Langlands Correspondence for algebraic tori.
The new ingredient in this proof is the geometrization of quasicharacters of algebraic tori over local fields,
which relies on the function--sheaf dictionary for smooth group schemes over finite fields developed recently by the authors.
We also use the class field theory of Serre and Hasewinkel.

Here is the main idea of the paper.
Let $K$ be a non-Archimedean local field with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
Let $T$ be an algebraic torus over $K$; we place no restriction on the ramification of $T$.
For every positive integer $n$, let $\GN{T}_n$ be the Greenberg transform of base change of the Neron model of $T$ to $\OK/\pK^n$,
where $\OK$ denotes the ring of integers of $K$ and $\pK$ is the maximal ideal in $\OK$.
Let $\QC(\GN{T}_n)$ be the rigid monoidal category of quasicharacter sheaves on $\GN{T}_n$,
obtained by applying the theory developed in [CR1] to the smooth commutative group scheme $\GN{T}_n$ over $\Fq$.
The category $\QC(\GN{T}_n)$ comes equipped with a canonical isomorphism
\[
\QCiso{\GN{T}_n} \to \Hom_{n}(T(K),\EEx)
\]
from the group of isomorphisms classes of quasicharacter sheaves on $\GN{T}_n$ to the group of quasicharacters of $T(K)$ of depth less than $n$ in Jiu-Kang Yu's filtration of $T(K)$.
In this paper we define a canonical isomorphism
\[
\QCiso{\GN{T}_n} \to H^1_{n}(\Weil{K},\hat{T}_\ell)
\]
to the group of Langlands parameters of depth less than $n$ in the upper-index filtration of the Weil group $\Weil{K}$.
We then verify that the local Langlands Correspondence matches $\chi \in \Hom_{n}(T(K),\EEx)$ with $\rho \in H^1_{n}(K,\hat{T}_\ell)$ if and only if $\chi$ and $\rho$ arise from the same quasicharacter sheaf on $\GN{T}_n$.
After passing from $\GN{T}_n$ to the group scheme $\GN{T} = \invlim{n} \GN{T}_n$, this shows that the local Langlands Correspondence for $T$ can be found within the category $\QC(\GN{T})$ of quasicharacter sheaves on $\GN{T}$.
\[
\begin{tikzcd}
\ & \arrow[swap]{dl}{} \QCiso{\GN{T}} \arrow{dr}{} & \\
\Hom_\text{qc}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(\Weil{K},\hat{T}_\ell)
\end{tikzcd}
\]

\subsection*{Old stuff}
While we have not yet fully explored the applications of such a geometrization, we want to highlight
some of the potential benefits of Theorem~\ref{thm:application} here.
Characters on $T$ have limited
functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
in the presence of maps from $T$ to other groups.  Sheaves, on the other hand, come
equipped with a host of functors, including pushforward.
We hope to use this to our advantage as we work toward an adaptation of
Lusztig's theory of characters sheaves to the study of characters of
admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.

@@

\section{The geometrization of quasicharacters of algebraic tori over local fields}

\subsection{Notations}

@@

\subsection{Greenberg of N\'eron}
\label{sec:GN}

@@

\subsection{The function--sheaf dictionary for quasicharacters of bounded depth}\label{sec:qcs}

In \cite{cunningham-roe:dictionary} we extended the function--sheaf dictionary of Deligne  \cite{deligne:SGA4.5}*{sommes trig.} to smooth commutative group schemes over finite fields.
Since we will use this dictionary here, we briefly review the main notation and result from that paper.

Let $G$ be a smooth commutative group scheme over $\Fq$ for which the geometric component group is finitely generated. A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; see \cite{cunningham-roe:dictionary}.
%
Quasicharacter sheaves on $G$ form a rigid monoidal category, denoted by $\QC(G)$
and the trace of Frobenius
\begin{equation}\label{snake}
  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
\end{equation}
  is a functorial isomorphism of groups \cite{cunningham-roe:dictionary}*{Thm. 11.1}.

@@

\subsection{A function--sheaf dictionary for quasicharacters} \label{sec:quasichar}

@@

\subsection{Application: Transfer of quasicharacter sheaves} \label{sec:transfer}

\subsection{Restriction of scalars over local fields}
\label{sec:wrK}

@@

\section{Parameters from quasicharacter sheaves}

The component group scheme $\pi_0(\GN{T}_n)$, which is independent of $n$, is defined by the short exact sequence
\[
\begin{tikzcd}
0 \arrow{r} & \GN{T}_n^0 \arrow{r}{\iota_0} & \GN{T}_n \arrow{r}{\pi_0} & \pi_0(\GN{T}_n) \arrow{r} & 0.
\end{tikzcd}
\]
As we saw in [CR], this exact sequence of smooth commutative group schemes defines an isomorphism of exact sequences of commutative groups
\[
\begin{tikzcd}
0 \arrow{r} & \QCiso{\pi_0(\GN{T}_n)} \arrow{r}{\pi_0^*} \arrow{d} & \QCiso{\GN{T}} \arrow{r}{\iota^*} \arrow{d} &  \QCiso{\GN{T}_n^0} \arrow{r} \arrow{d} & 0\\
0 \arrow{r} & \Hom(\pi_0(\GN{T}_n)(\Fq),\EEx) \arrow{r} & \Hom(\GN{T}_n(\Fq),\EEx) \arrow{r} & \Hom(\GN{T}_n^0(\Fq),\EEx) \arrow{r} & 0
\end{tikzcd}
\]
We have already seen $\Hom(\GN{T}_n(\Fq),\EEx) = \Hom_{<n}(T(K),\EEx)$;
by similar arguments,
\[
\Hom(\GN{T}^0_n(\Fq),\EEx) = \Hom_{<n}(T(\OK),\EEx).
\]
Consequently,
\[
\Hom(\pi_0(\GN{T}_n)(\Fq),\EEx) = \Hom(T(K)/T(\OK),\EEx).
\]
Our goal in the next three sections is to define the three dashed arrows below in the diagram below, in which the bottom row is the inflation-restriction sequence with the initial and terminal groups elided.
\[
\begin{tikzcd}[column sep=-5, row sep = 20]
&& & \arrow{dl} \QCiso{\pi_0(\GN{T}_n)} \arrow{rr} \arrow[dashed]{dd}[near start]{?} && \arrow{dl}  \QCiso{\GN{T}_n} \arrow[dashed]{dd}[near start]{?} \arrow{rr}  && \arrow{dl}  \QCiso{\GN{T}_n^\circ} \arrow[dashed]{dd}[near start]{?}  &  &  \\
&& \Hom(T(K)/T(\OK),\EEx)  \arrow[crossing over]{rr} \arrow{rd}{} && \Hom_{<n}(T(K),\EEx) \arrow[crossing over]{rr} \arrow{rd}{\text{rec}_T} && \Hom_{<n}(T(\OK),\EEx)  \arrow{rd}{}  &&  & \\
&&  & \Hh^1(\Weil{\Fq},\hat{T}_\ell^{I_K}) \arrow{rr} && \Hh^1_{<n}(\Weil{K},\hat{T}_\ell)\arrow{rr} && \Hh^1_{<n}(I_K,\hat{T}_\ell)^{\Weil{\Fq}} &  &
\end{tikzcd}
\]

\subsection{Component group}

There is another description of $\Hom(\pi_0(\GN{T}_n)(\Fq),\EEx)$ which leads easily to Langlands parameters for $T$:
\begin{eqnarray*}
\Hom(\pi_0(\GN{T}_n)(\Fq),\EEx)
&\iso & \Hom(\left(X_*(T)_{I_K}\right)^{\Weil{\Fq}},\EEx)\\
&\iso& \Hom(X_*(T)_{I_K},\EEx)_{\Weil{\Fq}}\\
&=& \Hh^1(\Weil{\Fq}, \Hom(X_*(T)_{I_K},\EEx)) \\
&\iso& \Hh^1(\Weil{\Fq}, \Hom(X_*(T),\EEx)^{I_K}) \\
&=& \Hh^1(\Weil{\Fq}, (X^*(T)\otimes_{\ZZ} \EEx)^{I_K}) \\
&=& \Hh^1(\Weil{\Fq}, \dual{T}_\ell^{I_K}).
\end{eqnarray*}

\subsection{Connected component}

\subsection{General case}

\section{Geometric reciprocity for tori over local fields}
\label{sec:reciprocity}

@@

\end{document}
%sagemathcloud={"zoom_width":100}
